Considering scale in multilayer animal social networks

### 2020-06-26 paper/manuscript.Rmd
intro p

<!-- intro -->
Animal social systems are characterized and influenced by three types of scale.
Social scale defines the type and measurement of social relationships and
directly impacts observed sociality between individuals. Spatial scale, in this
study, reflects the resolution of the habitat within which social interactions
occur. Finally, temporal scale is related to both study design and network
robustness as well as seasonal differences in resources, patch dynamics or
landscape connectivity. By parsing social systems into discrete contexts using
multilayer networks, we highlight the influence of social, spatial and temporal
scales on animal social systems, demonstrating the importance of considering
biologically relevant and robust observational scales.
<!-- intro -->

>>>>

<!-- intro -->
Animal social systems are characterized and influenced by scale.
Three types of scale to consider are social, spatial, and temporal scale.
Social scale defines the type and measurement of social relationships and
directly impacts observed social connectivity between individuals. Spatial scale 
can reflect the resolution of the habitat within which social interactions
occur. Finally, temporal scale is related to both study design and seasonal 
differences in social processes. By partitioning social associations into discrete contexts using
multilayer networks, we highlight the influence of social, spatial and temporal
scales on animal social systems, demonstrating the importance of considering
biologically relevant and robust scales.
<!-- intro -->
